---
title: "Coolest Thing I Learned"
author: "Rina Deka"
date: "2023-06-29"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
knitr::opts_chunk$set(echo = TRUE)
```

# The Most Interesting Thing i've Learned 

By far, one of the most interesting things I've learned was how to connect to and query an API.
Here's an example below, using an API Key "EefyNfm6f32hLdleNqk62NyYiIF5WmoTjCOIUxWl" from the NASA API.

## API Example: NASA Data

```{r,warning=FALSE}
library(tidyverse)
library(httr)
library(jsonlite)

url <- "https://api.nasa.gov/mars-photos/api/v1/rovers/curiosity/photos"
query_params <- list(sol = 1000, api_key = "EefyNfm6f32hLdleNqk62NyYiIF5WmoTjCOIUxWl")

response <- GET(url, query = query_params)

response
```
We connected to the computer that NASA has this on! Now let's get some data, let's say, the first thing from the data. It'll be parsed, too.
```{r}
if (http_type(NASA_Call) == "application/json") {
  data <- content(response, as = "parsed")}

data$photos[[1]]
```

Cool, huh? Check in next time!

